Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-08-03 sections/abstract.tex
Introduction edited, elaborated scalability in Results

\begin{abstract}
Modern Code Review (MCR) is a practice whereby reviewers virtually discuss proposed changes by adding comments through a code review tool or a mailing list. It has received much attention recently due to its perceived cost-effectiveness and popularity with industrial and OSS projects.
Recent studies have indicated a positive relationship between the number of review comments and code quality.
However, little research exists investigating how such discussion impacts software quality.
In fact, there has been concern that the informality of MCR encourages a focus on trivial, tangential, or unrelated issues.
Indeed, we have observed that such comments are quite frequent and may even constitute the majority.
We conjecture that an effective MCR actually depends on having a substantive quantity of comments that directly impact a proposed change (or are ``useful'').
To investigate this, a necessary step requires distinguishing review comments that are useful to a proposed change from those that are not.
For a large OSS project such as our Qt case study, manual assessment of the over 72,000 comments is a daunting task.
We propose that semantic similarity is a practical, cost-efficient, and empirically assurable approach for assisting with such assessments.
Our case-study results indicate that our approach can classify comments with an average F-measure score of 0.73 and reduce comment usefulness assessment effort by about 77\%.

>>>>

\begin{abstract}
Modern Code Review (MCR) is an informal practice whereby reviewers virtually discuss proposed changes by adding comments through a code review tool or mailing list. It has received much research attention due to its perceived cost-effectiveness and popularity with industrial and OSS projects.
Recent studies indicate there is a positive relationship between the number of review comments and code quality.
However, little research exists investigating how such discussion impacts software quality.
The concern is that the informality of MCR encourages a focus on trivial, tangential, or unrelated issues.
Indeed, we have observed that such comments are quite frequent and may even constitute the majority.
We conjecture that an effective MCR actually depends on having a substantive quantity of comments that directly impact a proposed change (or are ``useful'').
To investigate this, a necessary first step requires distinguishing review comments that are useful to a proposed change from those that are not.
For a large OSS projects such as our Qt case study, manual assessment of the over 72,000 comments is a daunting task.
We propose to utilize semantic similarity as a practical, cost-efficient, and empirically assurable approach for assisting with the manual usefulness assessment of MCR comments.
Our case-study results indicate that our approach can classify comments with an average F-measure score of 0.73 and reduce comment usefulness assessment effort by about 77\%.

### 2014-08-03 sections/introduction.tex
Introduction edited, elaborated scalability in Results

\section{Introduction}
Software code review is an established cost-effective software quality management practice.
Its main intent is to  identify  defects early and encourage quality development practices such as adherence to coding standards and improving code readability.
Nowadays less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industry and OSS projects.
One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
Reviewers can find problems in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
Developers then improve the changes in response to these comments and re-submit for review until the changes are approved.  
%Fig. \ref{fig:process} illustrates a typical MCR process.

Because performance of code review has a clear relationship to the quality of the software, many studies have investigated factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
However, little research exists investigating how review discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it is possible that they can either positively contribute to the proposed changes (i.e. are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e. relatively ``\emph{useless}''). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to look for trivial issues (e.g. coding styles), leaving deeper issues undiscussed \cite{Bacchelli2013a}.
%This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
This is a concern because a low-degree of useful comments can degrade the overall quality and perceived utility of MCR.

Prior research has focused mostly on the relation between number of comments and quality.
To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
One reason for this may be that to assess the impact of discussion in MCR, effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify their usefulness.
Moreover, comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible misinterpretation.

@@

In this paper, we present a text mining approach using semantic similarity to assist in classifying the usefulness of comments.
The proposed approach is meant to ease classifying large amounts of MRC comments in order to conduct comment and code quality studies (such as those discussed earlier) as manual classification can quickly become an untenable task.
By introducing automation support based on objective empirical criteria, our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
%Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
Through a case study of Qt project, we address the following research questions:
\begin{ResearchQuestions}
\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
\end{ResearchQuestions}

Our contributions are as follows:
\begin{itemize}
\item We propose a practical approach to mine natural text of comments in code reviews and classify their usefulness using semantic similarity.
\item We investigate relationship between usefulness of comments and semantic similarity.
\item We investigate cost-efficient, assurable and scalable of semantic similarity in large open source project based on actual human effort.
\end{itemize}

>>>>

\section{Introduction}
Software code review is a well-established software quality management practice.
Fundamentally the intent is to identify defects early and encourage quality development policy and practices such as adherence to coding standards and improving code readability.
Traditionally code reviews were a highly structured activity. Nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} are commonly used within both industry and OSS projects. 
One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
Reviewers can find problems in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
Developers then improve the changes in response to these comments and re-submit for review until the changes are approved.  
%Fig. \ref{fig:process} illustrates a typical MCR process. 
The popularity of MCR and readily available data have made it an attractive research area.  
In particular, because performance of code review has a clear relationship to the quality of the software, many studies have investigated the factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013} effectiveness.
However, little research exists investigating \emph{how} review discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it's possible that comments can either positively contribute to the proposed changes (i.e. are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e. relatively ``\emph{useless}''). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to focus on trivial issues (e.g. coding styles), leaving deeper and possibly more quality-important issues undiscussed \cite{Bacchelli2013a}.
%This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
This is a concern because a low-degree of useful comments may degrade the overall effectiveness and perceived utility of MCR.

Prior research has focused primarily on the relationship between number of comments and quality.
To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
One reason for this may be that to assess the impact of discussion in MCR, an effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
So while the data may be easy to access, MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to manually assess their usefulness.
Moreover, given that comments in MCR are unstructured natural text, open to subjective judgment, contain tacit understanding, and possible misinterpretation, assessment errors are inevitable.

@@

In this paper, we present a text mining approach using semantic similarity to assist in classifying the usefulness of comments.
As manual classification can quickly become an untenable task, our proposed approach is meant to ease classifying large amounts of MCR comments in order to conduct comment and code quality studies (such as those discussed earlier).
By introducing automation support for assessment grounded with objective empirical criteria, our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MCR data sets.
%Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
Hence through our case study of Qt project, in this work we explore the following research questions:
\begin{ResearchQuestions}
\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
\end{ResearchQuestions}

Our contributions are as follows:
\begin{itemize}
\item An investigation on the practicality of mining natural text comments in code reviews to classify their usefulness using semantic similarity.
\item Determination and validation of a model relating usefulness of comments and semantic similarity.
\item A case-study application and performance analysis of the model for a large open source project based (Qt) on actual human effort.
\end{itemize}

### 2014-08-03 sections/results.tex
Introduction edited, elaborated scalability in Results

\textbf{Scalability:} Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the table shows, the proportions are very similar in both the training dataset and all dataset,
which may suggest that our model will have a similar performance in the real data.

>>>>

\textbf{Scalability:} Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the table shows, the proportions are very similar in both the training dataset and all dataset. Indeed experiments for our case study using increasingly large random subsets of comments show the percentage of undetermined and overlap classification comments (and hence the manual effort required) is constant at about 23\%. While the percentage might vary for other projects, this result suggests that our method is scalable to very large numbers of comments. That is, the percentage of unclassified comments does not increase and hence we expect the method will reduce a substantial amount of manual assessment effort. This enables us to assess MCR comments for very large projects that currently are impractical to do without assistance. 
\dan{can we find a suitable example project to get some numbers for the example below?}
For example, OSS project XXX currently has YYY comments. Assuming constant effort and error rate (a dubious assumption), manual assessment effort for these would be estimated at ZZZ hours which is fundamentally impractical. However using similarity assessment with an estimated 23\% unclassified comments would reduce this effort to QQQ, a much more tractable effort.
